### 2025-05-08 chapters/arima2/child.Rnw
Changed paths in arima2/child, and workflow edits

<<armaSetup, include=FALSE,echo=FALSE,results='hide'>>=

@@

ma1_res <- readRDS("data/sim_MA1_results.rds")

@@

<<loadSimulation>>=
simulation1 <- readRDS("data/sim1_results.rds")

@@

<<getTiming>>=
sim_times <- readRDS("data/sim1_timing.rds")
mean_time <- sim_times$time.running %>% as.numeric() %>% mean()
@

@@

<<simTables>>=
simTables <- readRDS("data/sim2_AICtable_consistency.rds")
arma_inc <- simTables %>%
  filter(max_repeat == 1) %>%
  summarize(1 - sum(consistent, na.rm = TRUE) / n()) %>%
  unlist()
@

@@

theta_21 <- bake(
  file = 'data/PLCIsims.rds',
  {

@@

theta_1 <- bake(
  file = 'data/ar1sims.rds',
  {

@@

\section*{Supporting information}

\paragraph*{S1 Appendix}
\label{S_sampling}
{\bf Uniform Sampling.} An appendix demonstrating why uniform sampling of ARMA model parameters is impractical.

\paragraph*{S2 Appendix}
\label{S_python}
{\bf Python Comparison.} An appendix comparing our algorithm to existing Python software.

\paragraph*{S3 Source Files}
\label{S_simCode}
{\bf Source code and data} The manuscript was created as a dynamic document. All code and data used to create the article are included in this zipped folder.

\paragraph*{S4 R Package}
\label{S_source}
{\bf arima2, v3.3.0.} Source code of the \texttt{arima2} package used in this manuscript.

>>>>

<<armaSetup, include=FALSE,echo=FALSE,results='hide'>>=
# root <- paste0("chapters/arima2/")
root <- ""

@@

ma1_res <- readRDS(paste0(root, "data/sim_MA1_results.rds"))

@@

<<loadSimulation>>=
simulation1 <- readRDS(paste0(root, "data/sim1_results.rds"))

cat(paste0(root, "data/sim1_results.rds"))

@@

<<getTiming>>=
sim_times <- readRDS(paste0(root, "data/sim1_timing.rds"))
mean_time <- sim_times$time.running %>% as.numeric() %>% mean()
@

@@

<<simTables>>=
simTables <- readRDS(paste0(root, "data/sim2_AICtable_consistency.rds"))
arma_inc <- simTables %>%
  filter(max_repeat == 1) %>%
  summarize(1 - sum(consistent, na.rm = TRUE) / n()) %>%
  unlist()
@

@@

theta_21 <- bake(
  file = paste0(root, 'data/PLCIsims.rds'),
  {

@@

theta_1 <- bake(
  file = paste0(root, 'data/ar1sims.rds'),
  {

@@
